D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-01 ootavacuous.tex
Verifying Fundamental...: Add "the execution of"
The memory model allows reordering of loads after conditional
branches, so explicitly state that the ordering refers to the
execution (as opposed to the memory effects).

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
Global Analysis...: Qualify with "loose C++"
In contrast, a strict C++ compiler would need to keep the loads or
otherwise avoid the OOTA cycle.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Third case: $W'$ lies in the divergent portion of $H$.
This happens when $W'$ comes after the conditional or computed branch
which marks the end of the common period by going different ways in
$H$ and $G$.
Just as in the previous case, since the branch behaves differently in
the two executions it must be ordered after one of the $R'_i$ loads.
And then so must $W'$, because any instruction following a conditional-
or computed-branch instruction is ordered after that branch.
QED.

@@

void thread2() {
   int r2 = y;
   x = r2;
}
\end{verbatim}
\end{quote}
A compiler using global analysis and treating \co{x} and \co{y} as
quasi-volatile objects could omit the two loads, replacing them in the
machine code with simple assignments ``\co{r1 = 42}'' and
``\co{r2 = 42}''.
This would be a valid transformation, and the resulting behavior would
not count as OOTA according to our definition because the
dependencies in \co{thread1} and \co{thread2} would not be semantic.

>>>>

Third case: $W'$ lies in the divergent portion of $H$.
This happens when $W'$ comes after the conditional or computed branch
which marks the end of the common period by going different ways in
$H$ and $G$.
Just as in the previous case, since the branch behaves differently in
the two executions it must be ordered after one of the $R'_i$ loads.
And then so must $W'$, because the execution of any instruction following
a conditional- or computed-branch instruction is ordered after that
branch.
QED.

@@

void thread2() {
   int r2 = y;
   x = r2;
}
\end{verbatim}
\end{quote}
A loose C++ compiler using global analysis and treating \co{x} and \co{y} as
quasi-volatile objects could omit the two loads, replacing them in the
machine code with simple assignments ``\co{r1 = 42}'' and
``\co{r2 = 42}''.
This would be a valid transformation, and the resulting behavior would
not count as OOTA according to our definition because the
dependencies in \co{thread1} and \co{thread2} would not be semantic.
